---
title       : Speed Distance Prediction
subtitle    : 
author      : Ashish Lakhani
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

### Salient Features 


* Shiny application uses dataset cars to build a prediction model.
* App creates a model to calculate Distance required to stop car depending on its speed.
* Apps Asks user input for the speed at which their car is travelling.
* Uses Model to predict distance required to stop car at given speed.

--- &twocol

### Exploratory Analysis/Transformation

*** =left

```{r,echo=FALSE}
cars$sqrtdis=sqrt(cars$dist)
par(mfrow=c(2,2))
plot(cars$speed,cars$dist)
plot(cars$speed,cars$sqrtdis)
```

*** =right



* Plot on left is distance v/s speed.
* Plot on right is sqrt of distance v/s speed.
* Plot on right looks more linear so we will do transformation of distance for our analysis

---

### Final Model

```{r,echo=FALSE}
fit<-lm(sqrt(dist) ~ speed,data=cars)
summary(fit)
```

---

### Final Prediction


* Previous page displays summary of model we build.
* It predicts stopping distance in feet for cars at a given speed.
* In our shiny app We ask user to input speed of cars on left and provide distance required to stop as result.
* Final result obtained by multiplying speed with speed coefficient(.32241) and adding the intercept (1.277).
